Quantizing the Bosonic String on a Loop Quantum Gravity Background

### 2023-11-17 lqg-strings.tex
Swapped metrics for vielbeins in eqs(13) and (15)
Sketched X EoM and added the section for said EoM in the main file
Started new branch, added section on corrected Nambu-Goto action.

@@

Varying our action w.r.t connection $\omega ^{m n} _{c}$ gives the vanishing of world-sheet torsion $\mathcal{T}^{i} _{a b}$ as
\begin{equation} \label{eqn:variation-wrt-omega}
	\frac{\delta S_{P A}}{\delta \omega ^{m n} _{c}} \overset{!}{=} 0
\end{equation}
\begin{equation*}
	\downarrow
\end{equation*}
\begin{equation} \label{eqn:vanishing-torsion}
	\mathcal{T}^{i} _{a b} := e^{c i} D_{c} X^{\mu} _{k} v^{k} X^{\nu} _{[m} v_{n]} e^{m} _{a} e^{n} _{b} G_{\mu \nu} = 0 .
\end{equation}

@@

The equation of motion for the new field $v^{l}$ gives a constraint on said field and the embbeding fields $X^{\mu} _{i}$
\begin{equation} \label{eqn:variation-wrt-v}
	\frac{\delta S_{P A}}{\delta v^{l}} \overset{!}{=} 0
\end{equation}
\begin{equation*}
	\downarrow
\end{equation*}
\begin{equation} \label{eqn:v-and-X-constraint}
	g^{a b} D_{a} X^{\mu} _{l} D_{b} X^{\nu} _{j} v^{j} G_{\mu \nu} = 0 .
\end{equation}

>>>>

Before proceeding let us state our ``central dogma''. We take as physically well-motivated the central result of LQG that at the Planck scale well-defined geometric operators - such as those which measure the area and volume of a given region of space - exist, have discrete spectra and are gapped, \ie, the smallest eigenvalue is greater than zero. We now wish to understand how to construct a worldsheet action which will reflect this central dogma.

\section{Modified Nambu Goto Action}\label{sec:modified-ng}

In a very real sense string theory is a quantum theory of geometry. After all, the Nambu-Goto action:
\begin{equation}\label{eqn:ng-action}
	S_{NG} = -T \int d^2 x \sqrt{\det h}
\end{equation}
is nothing more than the \emph{area} of the string worldsheet. So when we are constructing the quantum theory of the string we are constructing a theory in which the fundamental excitations are geometric in nature. What we would like to do is to modify the string action in a way which incorporates the insight from LQG that at the Planck scale there is a minimum quantum of area. One simple way in which to do this is to modify the integrand in \eqref{eqn:ng-action} as follows:
\begin{equation*}
	\sqrt{h} \rightarrow \sqrt{h + g \Delta}.
\end{equation*}
Here, $g = l_{pl}/l_s$, where $l_{pl}$ is the Planck scale, the scale at which quantum geometric effects become important; $l_s$ is the string scale where quantum geometric effects due to area quantization become small; $\Delta$ is a constant which corresponds to the square of the minimal quantum of area. In the limit that $l_s \gg l_{pl}$, $g \ll 1$ and the string action reduces to the conventional Nambu-Goto action with small corrections coming from quantum geometry. In this limit we can expand the integrand as follows:
\begin{equation}
	\sqrt{h + g \Delta} \sim \sqrt{h}\left(1 + \frac{1}{2} \frac{g \Delta}{h} + \mc{O}(g^2/h^2)\right).
\end{equation}
Presumably the limit $g \ll 1$ corresponds to when the area of the string worldsheet is large compared to $\sqrt{h} \gg \Delta$. Thus in this limit $ g^2 \ll 1$ and $ h^2 \gg 1$ because of which we can drop the $\mc{O}(g^2/h^2)$ corrections. The final area corrected Nambu-Goto action becomes:
\begin{equation}
	S'_{NG} = -T \int d^2 x \left( \sqrt{h} +  \frac{1}{2} \frac{g \Delta}{\sqrt{h}} \right).
\end{equation}
This action has, to the best of our knowledge, not been explored in the string theory literature. However, such an inverse area term arises very naturally in the LQG approach and goes by the name of ``inverse triad'' corrections.

@@

Varying our action w.r.t connection $\omega ^{m n} _{c}$ gives the vanishing of world-sheet torsion $\mathcal{T}^{i} _{a b}$ as
\begin{equation} \label{eqn:variation-wrt-omega}
	\frac{\delta S_{P A}}{\delta \omega ^{m n} _{c}} \overset{!}{=} 0
\end{equation}
\begin{equation*}
	\downarrow
\end{equation*}
\begin{equation} \label{eqn:vanishing-torsion}
	\mathcal{T}^{i} _{a b} := e^{c i} D_{c} X^{\mu} _{k} v^{k} X^{\nu} _{[m} v_{n]} e^{m} _{a} e^{n} _{b} E^{I} _{\mu} E_{\nu I} = 0 .
\end{equation}

@@

The equation of motion for the new field $v^{l}$ gives a constraint on said field and the embbeding fields $X^{\mu} _{i}$
\begin{equation} \label{eqn:variation-wrt-v}
	\frac{\delta S_{P A}}{\delta v^{l}} \overset{!}{=} 0
\end{equation}
\begin{equation*}
	\downarrow
\end{equation*}
\begin{equation} \label{eqn:v-and-X-constraint}
	e^{a} _{i} e^{b i} D_{a} X^{\mu} _{l} D_{b} X^{\nu} _{j} v^{j} E^{I} _{\mu} E_{\nu I} = 0 .
\end{equation}

\subsection{The Embbeding Field Equation}

Finally, varying the action w.r.t the embbeding fields $X^{\lambda} _{l}$ yields a slightly modified version of the classical equation of motion for strings propagating in curved space-time:
\begin{equation} \label{eqn:variation-wrt-X}
	\frac{\delta S_{P A}}{\delta X^{\lambda} _{l}} \overset{!}{=} 0
\end{equation}
\begin{equation*}
	\downarrow
\end{equation*}
\begin{multline} \label{eqn:string-eom}
	e^{a} _{i} e^{b i} D_{b} (e v^{l} D_{a} X^{\mu} _{j} v^{j} E^{I} _{\mu} E_{\lambda I}) = \\
	= e e^{a} _{i} e^{b i} D_{a} X^{\mu} _{j} v^{j} D_{b} X^{\nu} _{k} v^{k} \frac{\partial E^{I} _{\mu}}{\partial X^{\lambda} _{l}} E_{\nu I} .
\end{multline}
